---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

# TL;dr
1. Many features need to be removed before any analysis are conducted. <br>
2. product variation inventory, merchant rating and merchang rating count seem to be the most important features. Those features about badges may also be helpful but there may be collinearity. <br>

```{r}
options(warn = -1)
library(dplyr)
library(tidyr)
#library(tidyverse)
library(GGally)
library(plotly)
library(cowplot)
library(ggcorrplot)
library(stringr)
```


```{r}
wish <- read.csv('summer-products-with-rating-and-performance_2020-08.csv')
```

```{r}
drops <- c('title', 'tags', 'crawl_month', 'theme', 'product_id', 'product_picture', 'product_url', 'merchant_id', 'merchant_profile_picture', 'merchant_info_subtitle', 'merchant_name', 'merchant_title', 'urgency_text', 'title_orig', 'shipping_option_name', 'currency_buyer')
wish <- wish[, !(names(wish) %in% drops)]

summary(wish)
```

# Data Cleaning
##checking NA's
1. Though there are 45 missing values in the details of rating count. It doesn't influence the rating count and average rating we want to look at, so maybe we can keep them for now (and it is very likely that we will drop the details of the rating count columns later) <br>
2. Replace 'na' in 'has_urgency_banner' with 0
```{r}
wish <- wish %>% mutate(has_urgency_banner = ifelse(is.na(has_urgency_banner), 0, has_urgency_banner))
wish$has_urgency_banner <- as.integer(wish$has_urgency_banner)
```

3. clean the sizes 
```{r}
wish <- wish %>%
  mutate(product_variation_size_id = tolower(product_variation_size_id)) %>%
  mutate(product_variation_size_id = gsub(pattern = '.', replacement = '',
                                          x = product_variation_size_id, fixed = TRUE)) %>%
  mutate(product_variation_size_id = gsub(pattern = '(size-*)|(size)', replacement = '',
                                          x = product_variation_size_id)) %>%
  mutate(product_variation_size_id = gsub(pattern = '.+[-]', replacement = '',
                                          x = product_variation_size_id)) %>%
  mutate(product_variation_size_id = ifelse(grepl(pattern = 'xl',product_variation_size_id),
                                            'xl', product_variation_size_id)) %>%
  mutate(product_variation_size_id = ifelse(grepl(pattern = 'xs', product_variation_size_id),
                                            'xs', product_variation_size_id)) %>%
  mutate(product_variation_size_id = str_replace(product_variation_size_id, ' ', '')) %>%
  mutate(product_variation_size_id = ifelse(product_variation_size_id %in% c('s', 'xs', 'm', 'l', 'xl'),
                                            product_variation_size_id, 'One-sized'))
```

```{r}
unique(wish['product_variation_size_id'])
```


5. fix the color. group the similar clours together. <br>
One thing might be worth looking at is ... whether special colors (not the mainstream ones) actually sell better, because they make people feel special?
```{r}
wish <- wish %>% 
    mutate(product_color = tolower(product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'red|burgundy|claret|wine|jasper', product_color),
                                  'red', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'blue|navy', product_color),
                                  'blue', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'white', product_color),
                                  'white', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'green|army', product_color),
                                  'green', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'black', product_color),
                                  'black', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'yellow|leopard|gold', product_color),
                                  'yellow', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'pink|rose', product_color),
                                  'pink', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'grey|gray|silver', product_color),
                                  'gray', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'purple|violet', product_color),
                                  'purple', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'orange|apricot', product_color),
                                  'orange', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'beige|nude|ivory|coffee|brown|khaki|camel',
                                        product_color), 'khaki', product_color)) %>%
    mutate(product_color = ifelse(grepl(pattern = 'floral|multicolor|camouflage|rainbow|star',
                                        product_color), 'multicolor', product_color))

wish['product_color'][wish['product_color'] == ''] <- 'Not defined'

wish['origin_country'][wish['origin_country'] == ''] <- 'Not defined'
```

6. handle with NA in rating columns
```{r}
wish$rating_five_count[which(is.na(wish$rating_five_count))] <- 0
wish$rating_four_count[which(is.na(wish$rating_four_count))] <- 0
wish$rating_three_count[which(is.na(wish$rating_three_count))] <- 0
wish$rating_two_count[which(is.na(wish$rating_two_count))] <- 0
wish$rating_one_count[which(is.na(wish$rating_one_count))] <- 0
wish$rating[which(wish$rating_count == 0)] <- 0
```

```{r}
# check for the number of unique values for each column 
# looks fine - we are good for the next steps
ulst <- lapply(wish, unique)
lengths(ulst)
```

7. factors

We check how many factors in each factor columns because we need to be careful when we split data. Error might occur if factor is in the test set but not in the training set. We also examine columns with only 0 and 1 records.

```{r}
str(wish)
```

```{r}
wish %>% 
  group_by(uses_ad_boosts) %>%
  summarise(no_rows = length(uses_ad_boosts)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(badges_count) %>%
  summarise(no_rows = length(badges_count)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(badge_local_product) %>%
  summarise(no_rows = length(badge_local_product)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(badge_product_quality) %>%
  summarise(no_rows = length(badge_product_quality)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(badge_fast_shipping) %>%
  summarise(no_rows = length(badge_fast_shipping)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(product_color) %>%
  summarise(no_rows = length(product_color)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(product_variation_size_id) %>%
  summarise(no_rows = length(product_variation_size_id)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(shipping_is_express) %>%
  summarise(no_rows = length(shipping_is_express)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(has_urgency_banner) %>%
  summarise(no_rows = length(has_urgency_banner)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(origin_country) %>%
  summarise(no_rows = length(origin_country)) %>%
  arrange(desc(no_rows)) 

wish %>% 
  group_by(merchant_has_profile_picture) %>%
  summarise(no_rows = length(merchant_has_profile_picture)) %>%
  arrange(desc(no_rows)) 
```

shipping_is_express has too many zero, so we decided to exclude this column. Also, product_color and origin_country might cause an error in prediction, so we need to change some record.

```{r}
wish <- select(wish, -c(shipping_is_express))
```

Only 7 colors have more than 100 records so We decided to keep only 8 factors of color, i.e. black, white, blue, red, green, yellow, pink and others.

```{r}
color_list <- c('black', 'white', 'blue', 'red', 'green', 'yellow', 'pink')
wish$product_color[!(wish$product_color %in% color_list)] <- 'others'

wish %>% 
  group_by(product_color) %>%
  summarise(no_rows = length(product_color)) %>%
  arrange(desc(no_rows)) %>%
  filter(no_rows > 100)
```

We decided to change origin to CN and others.

```{r}
wish$origin_country <- as.character(wish$origin_country)
wish$origin_country[which(wish$origin_country != 'CN')] <- 'others'
wish$origin_country[is.na(wish$origin_country)] <- 'others'

wish %>% 
  group_by(origin_country) %>%
  summarise(no_rows = length(origin_country)) %>%
  arrange(desc(no_rows)) 
```


```{r}
str(wish)
```

change columns' name

```{r}
origin_colname <- colnames(wish)
colnames(wish) <- c('price', 'retail', 'sold_ct', 'ad_boost', 'rate', 'rate_ct', 'rate5', 'rate4', 'rate3', 'rate2', 'rate1', 'badge_ct', 'bg_local', 'bg_quality', 'bg_fastship', 'color', 'size', 'inventory', 'ship_price', 'able_country', 'total_invent', 'has_bg_urgency', 'origin', 'seller_rate_ct', 'seller_rate', 'has_seller_propic')
```

# correlation plot
```{r, fig.width = 6, fig.height = 6}
library(corrplot)
# finding correlation between numeric columns and charges

numeric.column <- sapply(wish, is.numeric)
corr <- cor(wish[, numeric.column]) #, use = 'pairwise.complete.obs'
corrplot(corr, method = 'color')
```

# Feature Engineering 
1. Check for correlations 
```{r}
# cnr = wish %>% select(where(is.numeric)) %>% cor()
# #p-values matrix
# p.values = cor_pmat(wish %>% select(where(is.numeric)))
# 
# ggcorrplot(cnr, hc.order = TRUE, type = "lower",
#    outline.col = "black",
#    ggtheme = standard_theme,
#    colors = c('#d8b365', "white", "#de2d26"),p.mat=p.values,lab = TRUE)

# install.packages("corrplot")
# rquery.cormat(wish, type="upper")

#res <- wish %>% drop_na(rate5) %>% select(where(is.numeric)) %>% cor() # I have error for this line
res <- wish %>% drop_na(rate5) %>% select_if(is.numeric) %>% cor()
round(res, 2)
```

```{r, fig.width = 6, fig.height = 6}

#cnr <- wish %>% drop_na(rate5) %>% select(where(is.numeric)) %>% cor()
cnr <- wish %>% drop_na(rate5) %>% select_if(is.numeric) %>% cor()
#p-values matrix
p.values <- cor_pmat(wish %>% select_if(is.numeric))

ggcorrplot(cnr, hc.order = TRUE, type = 'lower',
           outline.col = 'black',
           # ggtheme = standard_theme,
           colors = c('#d8b365', 'white', '#de2d26'), p.mat = p.values) #, lab = TRUE)
```

Zooming in the plot and we can find - <br>
- strong positive correlation between: shipping option price vs price vs product variation inventory, merchant has profile picture vs shipping option price, rating_X_count has strong correlations with each other, badge fast shipping vs shipping is express (keeping one is enough), countries ship to vs shipping is express , badge product quality vs badge local product, rating vs badges count <br>
- strong negative correlation between: inventory total vs shipping is express vs price <br>
- unexpected correlations: price vs retail price (a lot of discount?), ad boost has barely no correlations with rating or units sold
```{r, fig.width = 8, fig.height = 8}
library(corrplot)
corrplot(res, type = 'upper', order = 'hclust', 
         tl.col = "black", tl.srt = 45)

```

```{r}
#wish <- wish %>% mutate(badge_ct = factor(badge_ct), ship_price = factor(ship_price)) # %>% select(-total_invent)

wish$has_bg_urgency <- as.integer(wish$has_bg_urgency)
wish <- wish %>% mutate_if(is.character, as.factor)

str(wish)
```

We plotted histogram to see the distribution of our response.

```{r}
library(rcompanion)
plotNormalHistogram(wish$sold_ct, main = 'Sold Count Histogram', xlab = 'Sold Count')
# since our sold_ct is right-skewed, we try performing log transfromation on it to make it normal distribution
plotNormalHistogram(log(wish$sold_ct), main = 'log(Sold Count) Histogram', xlab = 'log(Sold Count)') 
```

We split our dataset into a training set and a test set with 50:50 ratio.

```{r}
set.seed(123)
train_rows <- sample(1:nrow(wish), 0.5 * nrow(wish))
wish.train <- wish[train_rows, ] # wish training set
wish.test <- wish[-train_rows, ]
```

# Simple Linear Regression

```{r}
library(leaps)
# exhaustive search
regfit.full <- regsubsets(log(sold_ct) ~ ., data = wish.train)
reg.summary <- summary(regfit.full)

n.full <- c(which.min(reg.summary$cp), which.min(reg.summary$bic), which.max(reg.summary$adjr2))
coef(regfit.full, min(n.full))
```

```{r}
# forward stepwise selection
regfit.fwd <- regsubsets(log(sold_ct) ~ ., data = wish.train, method = 'forward')
n.fwd <- c(which.min(summary(regfit.fwd)$cp), which.min(summary(regfit.fwd)$bic), which.max(summary(regfit.fwd)$adjr2))
coef(regfit.fwd, min(n.fwd))

# backward stepwise selection
regfit.bwd <- regsubsets(log(sold_ct) ~ ., data = wish.train, method = 'backward')
n.bwd <- c(which.min(summary(regfit.bwd)$cp), which.min(summary(regfit.bwd)$bic), which.max(summary(regfit.bwd)$adjr2))
coef(regfit.bwd, min(n.bwd))
```

```{r}
set.seed(123)

# from exhaustive search
model1 <- lm(log(sold_ct) ~ price + rate + rate5 + rate2 + badge_ct + size + ship_price + able_country, data = wish.train)
# adjusted R-squared
summary(model1)$adj.r.squared

model1.pred <- predict(model1, wish.test) 
# test mse 
mse_model1 <- mean((log(wish.test$sold_ct) - model1.pred)^2) 
mse_model1

# from forward stepwise selection
model2 <- lm(log(sold_ct) ~ price + rate + rate_ct + rate2 + badge_ct + size + ship_price + able_country, data = wish.train)
# adjusted R-squared
summary(model2)$adj.r.squared

model2.pred <- predict(model2, wish.test) 
# test mse 
mse_model2 <- mean((log(wish.test$sold_ct) - model2.pred)^2) 
mse_model2

# from backward stepwise selection
model3 <- lm(log(sold_ct) ~ rate + rate_ct + rate5 + rate4 + rate3 + rate2 + size + ship_price + able_country, data = wish.train)
# adjusted R-squared
summary(model3)$adj.r.squared

model3.pred <- predict(model3, wish.test) 
# test mse 
mse_model3 <- mean((log(wish.test$sold_ct) - model3.pred)^2) 
mse_model3
```

The best linear regression model is the model 3 which is from backward stepwise selection.

```{r}
set.seed(123)

x.train <- select(wish.train, -c(sold_ct))
x.train <- data.matrix(x.train)
y.train <- wish.train[, 'sold_ct']
x.test <- select(wish.test, -c(sold_ct))
```

We fitted a lasso model because it has variable selection property.

```{r}
library(glmnet)
set.seed(123)
# find optimal lambda
lasso_model <- cv.glmnet(x.train, log(y.train), alpha = 1)
best_lambda_L <- lasso_model$lambda.min

# fit a lasso model on the training set
lasso_model2 <- glmnet(x.train, log(y.train), alpha = 1, lambda = best_lambda_L)
lasso.pred <- predict(lasso_model2, newx = data.matrix(x.test), s = best_lambda_L)
# test error
mse_L <- mean((log(wish.test$sold_ct) - lasso.pred)^2)
mse_L

# calcuate adjusted R-squared
totalSS <- mean((log(wish.test$sold_ct) - mean(log(wish.test$sold_ct)))^2) 
r2_L <- 1 - mse_L / totalSS 
r2_L
```

We tried using PCR model and PLS model too.

```{r}
library(pls)
set.seed(123)
# perform cross-validation to chose M
pcr_model <- pcr(log(sold_ct) ~ ., data = wish.train, scale = TRUE, validation = "CV")
summary(pcr_model)
validationplot(pcr_model, val.type = 'MSEP')

pcr.pred <- predict(pcr_model, wish.test, ncomp = 31)
# test error
mse_pcr <- mean((log(wish.test$sold_ct) - pcr.pred)^2)
mse_pcr

# adjusted R-squared
r2_pcr <- 1 - mse_pcr / totalSS 
r2_pcr
```

```{r}
set.seed(123)
# perform cross-validation to chose M
pls_model <- plsr(log(sold_ct) ∼ ., data = wish.train, scale = TRUE, validation = "CV")
summary(pls_model)
validationplot(pls_model, val.type = 'MSEP')

# fit a PLS model on the training set
pls.pred <- predict(pls_model, wish.test, ncomp = 14)
# test error
mse_pls <- mean((log(wish.test$sold_ct) - pls.pred)^2)
mse_pls

# adjusted R-squared
r2_pls <- 1 - mse_pls / totalSS 
r2_pls
```

Then, we compared test MSE from each model.

```{r, fig.height = 4}
# plot all test errors
mse_all <- c(mse_model3, mse_L, mse_pcr, mse_pls)
mse <- formatC(mse_all, digits = 4, format = 'f')
method <- c('Final lm', 'Lasso', 'PCR', 'PLS')

mse_table <- data.frame(mse_all, method)
mse_table$method <- factor(mse_table$method, levels = mse_table$method)
ggplot(mse_table, aes(x = method, y = mse_all)) + geom_bar(stat = 'identity') + xlab('Method') + ylab('Test MSE') + geom_text(aes(label = mse), vjust = 1.6, color = 'white', size = 4) + theme_light(base_size = 15)
```

```{r, fig.height = 4}
# compare adjuated R-squared
r2 <- c(summary(model3)$adj.r.squared, r2_L, r2_pcr, r2_pls)
r2_2 <- formatC(r2, digits = 4, format = 'f')

r2_table <- data.frame(r2, method)
r2_table$method2 <- factor(r2_table$method, levels = r2_table$method)

ggplot(r2_table, aes(x = method, y = r2)) + geom_bar(stat = 'identity') + xlab('Method') + ylab('Adjusted R-Squared') + geom_text(aes(label = r2_2), vjust = 1.6, color = 'white', size = 4) + theme_light(base_size = 15)
```



Non-parametric Methods

# Tree Models

```{r, fig.width = 6, fig.height = 4}
library(rpart)
library(rpart.plot)
set.seed(123)

# doing tree regression on log(y) ~ every x
tree.wish <- rpart(log(sold_ct) ~ ., data = wish.train) 
summary(tree.wish)
tree.wish$variable.importance

rpart.plot(tree.wish, type = 1, extra = 1, cex = 0.75)

predictions <- predict(tree.wish, wish.test)
# summarize accuracy
mse_tree <- mean((log(wish.test$sold_ct) - predictions)^2)
mse_tree 
```

# bagging

```{r}
library(ipred)
set.seed(123)

bag <- bagging(
   formula = log(sold_ct) ~ .,
   data = wish.train,
   nbagg = 100,  # interations included in the bagged model
   coob = TRUE, # out of bag sample, faster than CV
   control = rpart.control(minsplit = 2, cp = 0),
 )
bag

# predictions
bag_pred <- predict(bag, wish.test) 
#mse
mse_bag <- mean((log(wish.test$sold_ct) - bag_pred)^2)
mse_bag
```

# random forest

```{r}
library(randomForest)
library(ranger)
set.seed(123)

# number of features
n_features <- length(wish.train) - 1

# train a default random forest model
rf <- ranger(
  log(sold_ct) ~ ., 
  data = wish.train,
  mtry = floor(n_features / 3),
  respect.unordered.factors = 'order',
)

# get OOB MSE
mse_rf <- rf$prediction.error
mse_rf
```

# GBM

```{r}
library(gbm) 
set.seed(123)
  
# run a basic GBM model
set.seed(123)  # for reproducibility
wish_gbm <- gbm(
  formula = log(sold_ct) ~ .,
  data = wish.train,
  distribution = 'gaussian',  # SSE loss function
  n.trees = 5000,
  shrinkage = 0.1,
  interaction.depth = 3,
  n.minobsinnode = 10,
  cv.folds = 10
)

# find index for number trees with minimum CV error
best <- which.min(wish_gbm$cv.error)

# get MSE and compute RMSE
wish_gbm$cv.error[best]

# plot error curve
perf <- gbm.perf(wish_gbm, method = 'cv')

prediction_1 <- stats::predict(
                          # the model from above
                          object = wish_gbm, 
                          # the testing data
                          newdata = wish.test,
                          # this is the number we calculated above
                          n.trees = perf)

rmse_fit1 <- Metrics::rmse(actual = log(wish.test$sold_ct), 
                           predicted = prediction_1)

mse_gbm <- rmse_fit1^2
mse_gbm
```

```{r, fig.width = 5, fig.height = 4}
mse_all2 <- c(mse_tree, mse_bag, mse_rf, mse_gbm)
mse2 <- formatC(mse_all2, digits = 4, format = 'f')
method2 <- c('Tree', 'Bagging', 'Random Forests', 'GBM')

mse_table2 <- data.frame(mse_all2, method2)
mse_table2$method2 <- factor(mse_table2$method2, levels = mse_table2$method2)

ggplot(mse_table2, aes(x = method2, y = mse_all2)) + geom_bar(stat = 'identity') + xlab('Method') + ylab('Test MSE') + geom_text(aes(label = mse2), vjust = 1.6, color = 'white', size = 4) + theme_light(base_size = 15)
```




# svm with categorical sold_ct
```{r}
set.seed(1)

table(wish['sold_ct']) # very unbalaned
wish_cate = wish
wish_cate$sold_ct_cate = wish_cate$sold_ct
wish_cate$sold_ct_cate[which(wish_cate$sold_ct <=50)] <- 'below 50'
wish_cate$sold_ct_cate[which(wish_cate$sold_ct >=20000)] <- 'above 20K'
wish_cate = select(wish_cate, -sold_ct)
wish_cate$sold_ct_cate = as.factor(wish_cate$sold_ct_cate)
table(wish_cate$sold_ct_cate) # much better


train_index = sample(nrow(wish_cate), 1258) #around 80% of obs
wish.train = wish_cate[train_index, ]
wish.test = wish_cate[-train_index, ]

library(e1071)

set.seed(120)

tuned = tune(svm, sold_ct_cate ~ ., data = wish.train, kernel = "linear", ranges =list(cost = append(seq(0.01,10,by=0.5),10)))
summary(tuned) #cost = 8.51 is best
```

```{r}
lin.svm = svm(sold_ct_cate ~ ., kernel = "linear", data = wish.train, cost = 8.51)

train_pred = predict(lin.svm, wish.train)
table =table(wish.train$sold_ct_cate, train_pred)

print("training error with cost = 8.51: ")
(table[2]+table[3]) /(sum(table[1:4]))

test_pred = predict(lin.svm, wish.test)
table =table(wish.test$sold_ct_cate, test_pred)

print("training error with cost = 8.51: ")
(table[2]+table[3]) /(sum(table[1:4]))


```




# Model building with h2o
hasn't started yet because can't install the package
```{r}
# train.h2o <- as.h2o(wish.train)
# test.h2o <- as.h2o(wish.test)
```









```{r}
# check for the number of unique values for each column 
# ulst <- lapply(wish, unique)
# lengths(ulst)
```



```{r}


```




```{r}


```


